Quantifying the rock-paper-scissors effect

### 2022-06-28 inst/rock_paper_scissors_monster.Rmd
more likelihood plots

And try a profile likelihood:

@@

```{r,label=proflikh3,cache=TRUE}
lam <- seq(from=0.8,to=2.6,len=15)
like3 <- sapply(lam,profl)
like3 <- like3-max(like3)
```

```{r,plotproflike3}
plot(lam,like3,type='b')
abline(h=c(0,-2))
abline(v=1)
```

>>>>

@@

First optimize the likelihood:

```{r,optlike,cache=TRUE}
o <- optimize(profl,c(1.4,1.6),maximum=TRUE)
```

```{r}
o
```

So now plot a profile likelihood curve:

```{r,label=proflikh3,cache=TRUE}
lam <- seq(from=0.8,to=2.6,len=30)
like3 <- sapply(lam,profl)
```

```{r,plotproflike3}
plot(lam,like3-o$objective,type='b',ylab="likelihood",xlab="lambda")
abline(h=c(0,-2))
abline(v=c(1,o$maximum))
```
